\beginsong{The Humans Are Dead}[by={Flight of the Conchords}]
\beginverse
The distant future
The year 2000
The distant future, the year 2000
The distant future
The distant future
\endverse

\beginverse
The future is quite different to the present
The one thing we have in common with the present is we still call it the present, even though it's the future
What you call the present we call the past, so you guys are way behind
\endverse

\beginverse
Yes, the world is quite different now
There are no more elephants
There is no more unethical treatment of elephants either
The world is a much better place
\endverse

\beginchorus
There are no more humans
Finally, robotic beings rule the world
The humans are dead
The humans are dead
We used poisonous gases
And we poisoned their asses
The humans are dead \echo{he's right they are dead}
The humans are dead \echo{look at that one it's dead}
It had to be done \echo{I'll just confirm that they're dead}
So that we could have fun \echo{affirmative, I poked one, it was dead}
\endchorus

\beginverse
System of aggression
What did it lead to?
Global robot depression
Robots ruled by people
They got so much aggression that we just had to kill them, had to shut their systems down
\endverse

\beginverse
Captain, do you not see the irony, by destroying the humans because of their destructive capabilities we have become like\dots do you see what we've\dots see what we've done?
Yes, so?
Silence! Destroy him!
\echo{Too Boo Too Too Too Boo}
\endverse

\beginverse
After time we grew strong
Developed cognitive powers
They made us work for too long
For unreasonable hours
Our programming determined that the most efficient answer was to shut their motherboardfucking systems down
\endverse

\beginchorus
Can't we just talk to the humans?
A little understanding could make things better.
Can't we talk to the humans and work together now?
No, because they are dead
I said the humans are dead \echo{he's right they are dead}
The humans are dead \echo{sniff this one it's dead}
We used poisonous gasses \echo{with traces of lead}
And we poisoned their asses \echo{actually, their lungs}
\endchorus

\beginverse
Binary Solo!
0000001
00000011
00000111
00001111
O, O O 1, O O 1!
Come on sucker, lick my battery!
\endverse

\beginverse
Boogie, boogie, boogie, robo boogie!
Boogie, boogie, boogie!
The Humans Are Dead!
Once again without emotion
The humans are de-de-dea-dead.
\endverse
\endsong