\beginsong{Clementine}
\beginverse
In a cavern, In a canyon, 
Excavating for a mine, 
Dwelt a miner forty-niner, 
And his daughter Clementine.
\endverse

\beginchorus
Oh my darling, Oh my darling, 
Oh my darling Clementine, 
You are lost and gone forever, 
Dreadful sorry Clementine.
\endchorus

\beginchorus
Oh my darling, Oh my darling, 
Oh my darling Clementine, 
You are lost and gone forever, 
Dreadful sorry Clementine.
\endchorus

\beginverse
Light she was and like a fairy, 
And her shoes were number nine; 
Herring boxes, without topses, 
Sandals were for Clementine.
\endverse

\beginchorus
Oh my darling, Oh my darling\dots
\endchorus

\beginverse
Drove she ducklings to the water, 
Every morning just at nine; 
Hit her foot against a splinter, 
Fell into the foaming brine.
\endverse

\beginverse
Ruby lips above the water, 
Blowing bubbles, soft and fine; 
But Alas! I was no swimmer, 
So I lost my Clementine.
\endverse

\beginchorus
Oh my darling, Oh my darling\dots
\endchorus

\beginverse
When the miner forty-niner,
Soon began to peak and pine,
Thought he oughter "jine" his daughter,
Now he's with his clementine.
\endverse

\beginchorus
Oh my darling, Oh my darling\dots
\endchorus

\beginverse
In a corner of the churchyard,
Where the myrtle boughs entwine,
Grow the roses in their poses,
Fertilized by Clementine.
\endverse

\beginchorus
Oh my darling, Oh my darling\dots
\endchorus

\beginverse
In my dreams she still doth haunt me,
Robed in garments soaked in brine.
Though in life I used to hug her,
Now she's dead, I'll draw the line.
\endverse

\beginchorus
Oh my darling, Oh my darling\dots
\endchorus

\beginverse
How I missed her, how I missed her
How I missed my Clementine.
So I kissed her little sister,
And forgot my Clementine.
\endverse

\beginchorus
Oh my darling, Oh my darling\dots
\endchorus

\beginverse
Now you Boy Scouts, there's a moral
To this little tale of mine.
Artificial respiration,
Would have saved my Clementine.
\endverse

\beginchorus
Oh my darling, Oh my darling\dots
\endchorus
\endsong
