\beginsong{Roll Me Over}
\beginverse
This is number one and the fun has just begun
\endverse

\beginchorus
Roll me over lay me down and do it again
(Women yell) I like this feeling
Roll me over, in the clover
Roll me over, lay me down and do it again, again, again!
Do it again, again, again!
\endchorus

\beginverse
This is number two and my hand is on her shoe.
\endverse

\beginverse
This is number three and my hand is on her knee.
\endverse

\beginverse
This is number four and our clothes are on the floor.
\endverse

\beginverse
This is number five and the bee is in the hive.
\endverse

\beginverse
This is number six and I show her all my tricks.
\endverse

\beginverse
This is number seven and she says ``I am in heaven''.
\endverse

\beginverse
This is number eight and she starts to masturbate.
\endverse

\beginverse
This is number nine and I take her from behind.
\endverse

\beginverse
This is number ten and we do it once again.
\endverse

\beginverse
This is number eleven and she says ``Again from Seven''.
\endverse

\beginverse
This is number twelve and she says ``Do it yourself!''
\endverse

\beginverse
This is number thirteen and we dry us in the curtain.
\endverse

\beginverse
This is number twenty and the gun is getting empty.
\endverse

\beginverse
This is number thirty and this song is getting dirty.
\endverse

\beginverse
This is number forty and she says ``Now this is naughty!''
\endverse

\beginverse
This is number hundred and the neighbours start to wonder.
\endverse

\beginverse
This is number 1344 and she still wants some more\dots
\endverse
\endsong
