\beginsong{Always Look On the Bright Side of Life}[by={Monty Python}]
\beginverse
Some things in life are bad
They can really make you mad
Other things just make you swear and curse.
When you're chewing on life's gristle
Don't grumble, give a whistle
And this'll help things turn out for the best\dots
\endverse

\beginchorus
And\dots always look on the bright side of life\dots
Always look on the light side of life\dots
\endchorus

\beginverse
If life seems jolly rotten
There's something you've forgotten
And that's to laugh and smile and dance and sing.
When you're feeling in the dumps
Don't be silly chumps
Just purse your lips and whistle -- that's the thing.
\endverse

\beginchorus
And\dots always look on the bright side of life\dots
Always look on the light side of life\dots
\endchorus

\beginverse
For life is quite absurd
And death's the final word
You must always face the curtain with a bow.
Forget about your sin - give the audience a grin
Enjoy it -- it's your last chance anyhow.
\endverse

\beginchorus
So always look on the bright side of death
Just before you draw your terminal breath
\endchorus

\beginverse
Life's a piece of shit
When you look at it
Life's a laugh and death's a joke, it's true.
You'll see it's all a show
Keep 'em laughing as you go
Just remember that the last laugh is on you.
\endverse

\beginchorus
And always look on the bright side of life\dots
Always look on the right side of life\dots
\echo{Come on guys, cheer up!}
Always look on the bright side of life\dots
Always look on the bright side of life\dots
\echo{Worse things happen at sea, you know.}
Always look on the bright side of life\dots
\echo{I mean -- what have you got to lose?}
\echo{You know, you come from nothing -- you're going back to nothing. What have you lost? Nothing!}
Always look on the right side of life\dots
\endchorus
\endsong